\documentclass[11pt,conference]{IEEEtran}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{booktabs}

% Title and Author info
\title{CyberSage: A Multi-Agent AI System for Cyber Threat Intelligence}

\author{
  Team 9 \\
  Muhammad Faris Bin Noordin (A0291946N), 
  Lay Wee Lye (A0291952W), \\
  Michael Lee Ming Fung (A0291994J), 
  Cheah Kit Weng (A0059806W) \\
  National University of Singapore (NUS-ISS) \\
}

\begin{document}

\maketitle

\begin{abstract}
Security Operations Centers (SOCs) face increasing overload from heterogeneous threat intelligence feeds.
We present CyberSage, a modular four-agent system designed to automate ingestion, entity extraction, triage, and explainability in cyber threat intelligence pipelines.
CyberSage combines domain-adapted Named Entity Recognition (NER) with risk scoring informed by KEV/EPSS, explainability-first governance, and MLSecOps safeguards.
This paper outlines the design of each agent, their interactions, and their contribution to reliable, explainable, and actionable CTI.
\end{abstract}

\section{Introduction}
Timely and trustworthy cyber threat intelligence (CTI) is critical for modern SOCs.
Yet the CTI workflow remains fragmented: feeds are heterogeneous, entity extraction is error-prone, prioritization often ignores asset context, and analyst trust hinges on explainability.
Agentic AI architectures, especially when modular and evidence-grounded, offer a path forward.
CyberSage implements four autonomous agents:
(i) ingestion and normalization,
(ii) intelligence extraction (NER),
(iii) risk and triage,
(iv) assurance and explainability.
Together, they demonstrate modularity, domain adaptation, and responsible AI practices.

\section{System Overview}
CyberSage’s workflow is: raw sources $\rightarrow$ ingestion (Agent A) $\rightarrow$ entity extraction (Agent B) $\rightarrow$ risk scoring (Agent C) $\rightarrow$ assurance/explanation (Agent D) $\rightarrow$ analyst-facing dashboard.
Each agent is autonomous yet coordinated through a message bus and shared memory.
This modular design improves scalability, explainability, and resilience compared to monolithic chatbots or rule-based systems.

% --- Multi-Agent System Sections ---
\input{agentA_ingest}             % Agent A: Ingestion & Normalization
\input{agentB_ner}                % Agent B: Intelligence Extraction (NER Agent)
\input{agentC_risk_triage}        % Agent C: Risk & Triage
\input{agentD_assurance_explain}  % Agent D: Assurance & Explainability

\section{Conclusion}
CyberSage illustrates how a multi-agent architecture can operationalize domain-adapted NER, risk scoring, and explainability to address critical pain points in SOC workflows.
By combining structured entity extraction, evidence-grounded assurance, and MLSecOps safeguards, CyberSage demonstrates the potential of agentic AI systems for CTI.
Future work includes cross-lingual adaptation, knowledge-graph integration, and evaluation in production SOC environments.

\bibliographystyle{ieeetr}
\nocite{*}
\bibliography{CyberSage}

\end{document}
